---
title: "p8105_hw5_sdc2157"
author: "Stephanie Calluori"
date: 2023-11-15
output: github_document
---
load packages and set seed
```{r, message = FALSE}
library(tidyverse)
library(readr)
library(rvest)
library(httr)
library(patchwork)

set.seed(1)
```


```{r, message = FALSE, echo = FALSE, results = FALSE}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "right"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1

#Describe the Raw data:
```{r}
homicide_raw <- read_csv("data/homicide_data_copy.csv", col_names = TRUE)

#str(homicide_raw)
nrow(homicide_raw)
ncol(homicide_raw)
colnames(homicide_raw)

homicide_raw |> 
  count(uid) |> 
  arrange(desc(n))

```

ADD DESCRIPTION for raw data; rows, columns, variables; each row is a case; no double entries of cases


#Create a city_state variable (e.g. “Baltimore, MD”) and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).

victim_age is of class character so we made it a numeric
```{r}
homicide_clean <- homicide_raw |> 
  janitor::clean_names() |> 
  mutate(victim_age = as.numeric(victim_age)) |> 
  mutate(city_state = paste(city, state, sep = ",")) |> 
  mutate(disposition = recode(
    disposition,
    "Closed by arrest" = 0,
    "Closed without arrest" = 1,
    "Open/No arrest" = 1))

head(homicide_clean)

class(homicide_clean$victim_age)

homicide_clean |> 
  count(city_state) |> 
  nrow()

```

Total number of homicides in each city
```{r}
homicide_clean |> 
  count(city_state) |> 
  mutate(city_state = forcats::fct_reorder(city_state, n, .desc = TRUE)) |> 
  ggplot(aes(x = city_state, y = n)) + 
  geom_col() +
  labs(
    title = "Number of homicides in each city",
    x = "city",
    y = "Total # of homicides"
  ) +
  theme(axis.text.x = element_text(angle=90, vjust=1, hjust=1))

```


number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).
Number of unresolved homicides in each city
```{r}
homicide_clean |> 
  filter(disposition == 1) |> 
  count(city_state) |> 
  mutate(city_state = forcats::fct_reorder(city_state, n, .desc = TRUE)) |> 
  ggplot(aes(x = city_state, y = n)) + 
  geom_col() +
  labs(
    title = "Number of unresolved homicides in each city",
    x = "city",
    y = "# of unresolved homicides"
  ) +
  theme(axis.text.x = element_text(angle=90, vjust=1, hjust=1))

```

DESCRIBE Each Graph

If n> 30: prop.test(x, n, p = 0.5, alternative = “two.sided”, correct=TRUE)
For the city of Baltimore, MD, use the prop.test function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe.

Conducting a one sample test for proportions using prop.test
Is the proportion of unresolved cases in Baltimore different from 50%?
```{r}
baltimore_df <- homicide_clean |> 
  filter(city == "Baltimore")

num_successes <- baltimore_df |> 
  filter(disposition == 1) |> 
  nrow()

n_sample <- nrow(baltimore_df)

output <- prop.test(x = num_successes, n = n_sample, p = 0.5, alternative = "two.sided", conf.level = 0.95, correct = FALSE)

output |> 
  broom::tidy() |> 
  select(estimate, conf.low, conf.high)

#prop.test(x = num successes, n = total cases, p = 0.5, alternative = "two.sided", conf.level = 0.95, correct = FALSE)


#fit |> 
 # broom::tidy() |> 
  #select(term, estimate, p.value) |> 
 # mutate(term = str_replace(term, "^borough", "Borough: ")) |> 
 # knitr::kable(digits = 3)


```


Turn Baltimore example into a function to get estimate and CI for each city; then test the function

```{r}
estimate_and_CI <- function(city_df) {
  
successes <- city_df |> 
  filter(disposition == 1) |> 
  nrow()

sample_size <- nrow(city_df)

output <- prop.test(x = successes, n = sample_size, p = 0.5, alternative = "two.sided", conf.level = 0.95, correct = FALSE)

output |> 
  broom::tidy() |> 
  select(estimate, conf.low, conf.high)
  
}

estimate_and_CI(baltimore_df )

```


Now run prop.test for each of the cities in your dataset, and extract both the proportion of unsolved homicides and the confidence interval for each. Do this within a “tidy” pipeline, making use of purrr::map, purrr::map2, list columns and unnest as necessary to create a tidy dataframe with estimated proportions and CIs for each city.
```{r}
homicide_nest_df <- homicide_clean |> 
  select(city, everything()) |> 
  nest(.data = _, data = uid:city_state)

results <- homicide_nest_df |> 
  mutate(summary = map(data, estimate_and_CI)) |> 
  unnest(cols = summary) |> 
  select(city, estimate, conf.low, conf.high)

head(results)

#map(homicide_nest_df$data, estimate_and_CI)

```

Create a plot that shows the estimates and CIs for each city – check out geom_errorbar for a way to add error bars based on the upper and lower limits. Organize cities according to the proportion of unsolved homicides.

```{r}
results |> 
  mutate(city = forcats::fct_reorder(city, estimate, .desc = TRUE)) |> 
  ggplot(aes(x = city, y = estimate)) +
  geom_point() +
  geom_errorbar(
    aes(x = city,
        ymin = conf.low,
        ymax = conf.high)
  ) +
  labs(
    title = "Estimate of the proportion of unresolved homicides in each city",
    x = "city",
    y = "estimate of proportion of unresolved homicides"
  ) +
  theme(axis.text.x = element_text(angle=90, vjust=1, hjust=1))


```

# Problem 2
Start with a dataframe containing all file names; the list.files function will help
Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe

Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary

Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.


```{r, message = FALSE}
participant_list <- list.files("data/rct_data", full.names = TRUE)

participant_df <- participant_df <- tibble(file_name = participant_list) |> 
  mutate(all_obs = (map(file_name, \(f) read_csv(file = f)))) 

participant_clean <- participant_df |> 
  unnest(all_obs) |> 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "obs",
    names_prefix = "week_") |> 
  mutate(file_name = map(file_name, \(g) basename(g))) |> 
  unnest(file_name) |> 
  mutate(file_name = stringr::str_remove(file_name, ".csv")) |> 
  rename(id = file_name) |> 
  mutate(week = as.numeric(week)) |> 
  mutate(arm = stringr::str_sub(id, 1, 3)) |> 
  select(id, arm, week, obs)


```


Which plot to use?
```{r}
participant_clean |> 
  ggplot(aes(x = week, y = obs)) +
  geom_point(aes(color = id)) +
  geom_line(aes(color = id)) +
  geom_smooth(aes(color = arm), se = FALSE) 
  
participant_clean |> 
  ggplot(aes(x = week, y = obs)) +
  geom_point(aes(color = id)) +
  geom_line(aes(color = id)) +
  geom_smooth(se = FALSE) +
  facet_grid(~arm)
  

```

# Problem 3
 
One sample t test; two sided
*Change to 5000 runs; what to do about computer pausing when running? won't give next output
```{r}
t_test <- function(x) {
  t = t.test(x = x, mu = 0, conf.level = 0.95)
  
  broom::tidy(t)
}

simul_df <- 
  expand_grid(
    sample_size = 30,
    true_mean_u = 0:6,
    iter = 1:5000
  ) |> 
  mutate(simul_dataset = map2(sample_size, true_mean_u, \(sa, tmu) rnorm(n = sa, mean = tmu, sd = 5)))

simul_df <- simul_df |> 
  mutate(summary = map(simul_dataset, \(si) t_test(x = si))) |> 
  unnest(summary) |> 
  select(true_mean_u, estimate, p.value)

```
Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ
 on the x axis. Describe the association between effect size and power.

```{r}
simul_df |> 
  select(true_mean_u, estimate, p.value) |> 
  mutate(null_rejected = case_when(
    p.value <= 0.05 ~ "Yes",
    p.value > 0.05 ~ "No")) |>
  group_by(true_mean_u) |>
  count(null_rejected) |> 
  mutate(prop = n / sum(n)*100) |> 
  filter(null_rejected == "Yes") |> 
  ggplot(aes(x = true_mean_u, y = prop)) +
  geom_point() +
  labs(
    title = "Plot of power against mu",
    x = "mu",
    y = "power"
  )

```

As effect size increases, power increases.


Make a plot showing the average estimate of μ̂ 
 on the y axis and the true value of μ
 on the x axis. Make a second plot (or overlay on the first) the average estimate of μ̂ 
 only in samples for which the null was rejected on the y axis and the true value of μ
 on the x axis. Is the sample average of μ̂ 
 across tests for which the null is rejected approximately equal to the true value of μ
? Why or why not?


```{r}

all <- simul_df |> 
  select(true_mean_u, estimate) |> 
  group_by(true_mean_u) |> 
  summarize(avg_estimate_u = mean(estimate)) |> 
  ggplot(aes(true_mean_u, avg_estimate_u)) +
  geom_point() +
  geom_smooth(se = FALSE) +
  labs(
    title = "Plot of avg u_hat against mu",
    x = "mu",
    y = "average mu_hat"
  )

filtered <- simul_df |> 
  select(true_mean_u, estimate, p.value) |> 
  filter(p.value <= 0.05) |> 
  group_by(true_mean_u) |> 
  summarize(avg_estimate_u = mean(estimate)) |> 
  ggplot(aes(true_mean_u, avg_estimate_u)) +
  geom_point() +
  geom_smooth(se = FALSE) +
  labs(
    title = "Plot of avg u_hat against mu",
    subtitle = "Only when null hypotesis is rejected",
    x = "mu",
    y = "average mu_hat"
  )

all + filtered
```

better fit at higher values. why? greater effect size so more power?
power - rejecting the null when it is actually false
but when we reject the null we say it follows a diff distribution so they shouldn't match?



