---
title: "p8105_hw5_sdc2157"
author: "Stephanie Calluori"
date: 2023-11-15
output: github_document
---
load packages and set seed
```{r, message = FALSE}
library(tidyverse)
library(readr)
library(rvest)
library(httr)

set.seed(1)
```


```{r, message = FALSE, echo = FALSE, results = FALSE}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "right"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1

#Describe the Raw data:
```{r}
homicide_raw <- read_csv("data/homicide_data_copy.csv", col_names = TRUE)

#str(homicide_raw)
nrow(homicide_raw)
ncol(homicide_raw)
colnames(homicide_raw)

homicide_raw |> 
  count(uid) |> 
  arrange(desc(n))

```

ADD DESCRIPTION for raw data; rows, columns, variables; each row is a case; no double entries of cases


#Create a city_state variable (e.g. “Baltimore, MD”) and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).

victim_age is of class character so we made it a numeric
```{r}
homicide_clean <- homicide_raw |> 
  janitor::clean_names() |> 
  mutate(victim_age = as.numeric(victim_age)) |> 
  mutate(city_state = paste(city, state, sep = ",")) |> 
  mutate(disposition = recode(
    disposition,
    "Closed by arrest" = 0,
    "Closed without arrest" = 1,
    "Open/No arrest" = 1))

head(homicide_clean)

class(homicide_clean$victim_age)

homicide_clean |> 
  count(city_state) |> 
  nrow()

```

Total number of homicides in each city
```{r}
homicide_clean |> 
  count(city_state) |> 
  mutate(city_state = forcats::fct_reorder(city_state, n, .desc = TRUE)) |> 
  ggplot(aes(x = city_state, y = n)) + 
  geom_col() +
  labs(
    title = "Number of homicides in each city",
    x = "city",
    y = "Total # of homicides"
  ) +
  theme(axis.text.x = element_text(angle=90, vjust=1, hjust=1))

```


number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).
Number of unresolved homicides in each city
```{r}
homicide_clean |> 
  filter(disposition == 1) |> 
  count(city_state) |> 
  mutate(city_state = forcats::fct_reorder(city_state, n, .desc = TRUE)) |> 
  ggplot(aes(x = city_state, y = n)) + 
  geom_col() +
  labs(
    title = "Number of unresolved homicides in each city",
    x = "city",
    y = "# of unresolved homicides"
  ) +
  theme(axis.text.x = element_text(angle=90, vjust=1, hjust=1))

```

DESCRIBE Each Graph

If n> 30: prop.test(x, n, p = 0.5, alternative = “two.sided”, correct=TRUE)
For the city of Baltimore, MD, use the prop.test function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe.

Conducting a one sample test for proportions using prop.test
Is the proportion of unresolved cases in Baltimore different from 50%?
```{r}
baltimore_df <- homicide_clean |> 
  filter(city == "Baltimore")

num_successes <- baltimore_df |> 
  filter(disposition == 1) |> 
  nrow()

n_sample <- nrow(baltimore_df)

output <- prop.test(x = num_successes, n = n_sample, p = 0.5, alternative = "two.sided", conf.level = 0.95, correct = FALSE)

output |> 
  broom::tidy() |> 
  select(estimate, conf.low, conf.high)

#prop.test(x = num successes, n = total cases, p = 0.5, alternative = "two.sided", conf.level = 0.95, correct = FALSE)


#fit |> 
 # broom::tidy() |> 
  #select(term, estimate, p.value) |> 
 # mutate(term = str_replace(term, "^borough", "Borough: ")) |> 
 # knitr::kable(digits = 3)


```


Turn Baltimore example into a function to get estimate and CI for each city; then test the function

```{r}
estimate_and_CI <- function(city_df) {
  
successes <- city_df |> 
  filter(disposition == 1) |> 
  nrow()

sample_size <- nrow(city_df)

output <- prop.test(x = successes, n = sample_size, p = 0.5, alternative = "two.sided", conf.level = 0.95, correct = FALSE)

output |> 
  broom::tidy() |> 
  select(estimate, conf.low, conf.high)
  
}

estimate_and_CI(baltimore_df )

```


Now run prop.test for each of the cities in your dataset, and extract both the proportion of unsolved homicides and the confidence interval for each. Do this within a “tidy” pipeline, making use of purrr::map, purrr::map2, list columns and unnest as necessary to create a tidy dataframe with estimated proportions and CIs for each city.
```{r}
homicide_nest_df <- homicide_clean |> 
  select(city, everything()) |> 
  nest(.data = _, data = uid:city_state)

results <- homicide_nest_df |> 
  mutate(summary = map(data, estimate_and_CI)) |> 
  unnest(cols = summary) |> 
  select(city, estimate, conf.low, conf.high)

head(results)

#map(homicide_nest_df$data, estimate_and_CI)

```

Create a plot that shows the estimates and CIs for each city – check out geom_errorbar for a way to add error bars based on the upper and lower limits. Organize cities according to the proportion of unsolved homicides.

```{r}
results |> 
  mutate(city = forcats::fct_reorder(city, estimate, .desc = TRUE)) |> 
  ggplot(aes(x = city, y = estimate)) +
  geom_point() +
  geom_errorbar(
    aes(x = city,
        ymin = conf.low,
        ymax = conf.high)
  ) +
  labs(
    title = "Estimate of the proportion of unresolved homicides in each city",
    x = "city",
    y = "estimate of proportion of unresolved homicides"
  ) +
  theme(axis.text.x = element_text(angle=90, vjust=1, hjust=1))


```

# Problem 2
Start with a dataframe containing all file names; the list.files function will help
Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe

Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary


```{r, eval = FALSE}
participant_list <- list.files("data/rct_data", full.names = TRUE)

participant_df <- participant_df <- tibble(file_name = participant_list) |> 
  mutate(all_obs = (map(file_name, \(f) read_csv(file = f)))) 

w <- function(w) {
  basename(w)               

}

participant_tidy <- participant_df |> 
  unnest(all_obs) |> 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "obs",
    names_prefix = "week_") |> 
  mutate(file_name = map(file_name, w)) |> 
  unnest(file_name)

participant_tidy <- participant_df |> 
  unnest(all_obs) |> 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "obs",
    names_prefix = "week_") |> 
  mutate(file_name = map(file_name, \(g) basename(g))) |> 
  unnest(file_name)

participant_tidy <- participant_df |> 
  unnest(all_obs) |> 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "obs",
    names_prefix = "week_") |> 
  mutate(file_name = map(file_name, \(g) basename(g))) |> 
  unnest(file_name)


             
            
                 


str_extract(., "\\d_\\d" )

  
  participant_tidy <- participant_df |> 
  unnest(all_obs) |> 
  mutate(file_name = map(file_name, \(f) stringr::str_sub(string = file_name, 15, 20))) |> 
  unnest(file_name)
  
  
participant_df <- participant_df <- tibble(file_name = participant_list) |> 
  mutate(all_obs = (map(file_name, \(f) read_csv(file = f)))) |> 
  mutate(file_name = map(file_name, \(f) stringr::str_sub(string = file_name, 15, 20))) |> 
  unnest(file_name)
  
tail(participant_df)

  
  mutate(file_name = map(file_name, \(f) stringr::str_split(string = file_name, "."))) |> 
  unnest(file_name)

  str_split()
  mutate(arm_id = map(file_name, \(f) stringr::str_sub(string = file_name, 15, 20))) |> 
  unnest(arm_id)

  separate(file_name, into = c("a", "b"), sep = ".")
  
  
  mutate(file_name = map(file_name, \(f) substring(text = file_name, 15, 20))) |> 
  unnest(file_name)


         )
  mutate(id = map(file_name, \(f) substring(text = file_name, 18, 20))) |> 
  unnest(arm) |> 
  unnest(id)


  separate(file_name, into = c("arm", "id"), sep = 13)


tail(participant_tidy)

?substring()

  mutate(file_name = map(file_name, \(f) stringr::str_sub(string = file_name, 15, 20))) |> 


|> 
  select(arm_id, week, obs)
  separate(arm_id, into = c("arm", "id"), sep = "_") |> 
  select(id, arm, week, obs)

tail(participant_tidy)

  
stringr::str_sub("data/rct_data/con_01.csv", 15, 20)
?str_sub()
  gsub('data/rct/data/', file_name)

gsub('character', '', my_string)

  separate(file_name, into = c("arm", "id"), sep = 13)

?pivot_longer()
```












