---
title: "p8105_hw5_sdc2157"
author: "Stephanie Calluori"
date: 2023-11-15
output: github_document
---
load packages and set seed
```{r, message = FALSE}
library(tidyverse)
library(rvest)
library(httr)

set.seed(1)
```

setup
```{r, message = FALSE}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "right"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

#Describe the Raw data:
```{r}
homicide_raw <- read_csv("data/homicide_data_copy.csv", col_names = TRUE)

#str(homicide_raw)
nrow(homicide_raw)
ncol(homicide_raw)
colnames(homicide_raw)

homicide_raw |> 
  count(uid) |> 
  arrange(desc(n))

```

ADD DESCRIPTION for raw data; rows, columns, variables; each row is a case; no double entries of cases


#Create a city_state variable (e.g. “Baltimore, MD”) and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).

victim_age is of class character so we made it a numeric
```{r}
homicide_clean <- homicide_raw |> 
  janitor::clean_names() |> 
  mutate(victim_age = as.numeric(victim_age)) |> 
  mutate(city_state = paste(city, state, sep = ","))

head(homicide_clean)

class(homicide_clean$victim_age)

homicide_clean |> 
  count(city_state) |> 
  nrow()

```

Total number of homicides in each city
```{r}
homicide_clean |> 
  count(city_state) |> 
  mutate(city_state = forcats::fct_reorder(city_state, n, .desc = TRUE)) |> 
  ggplot(aes(x = city_state, y = n)) + 
  geom_col() +
  labs(
    title = "Number of homicides in each city",
    x = "city",
    y = "Total # of homicides"
  ) +
  theme(axis.text.x = element_text(angle=90, vjust=1, hjust=1))

```


number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).
Number of unresolved homicides in each city
```{r}
homicide_clean |> 
  filter(disposition == "Closed without arrest" | disposition == "Open/No arrest") |> 
  count(city_state) |> 
  mutate(city_state = forcats::fct_reorder(city_state, n, .desc = TRUE)) |> 
  ggplot(aes(x = city_state, y = n)) + 
  geom_col() +
  labs(
    title = "Number of unresolved homicides in each city",
    x = "city",
    y = "# of unresolved homicides"
  ) +
  theme(axis.text.x = element_text(angle=90, vjust=1, hjust=1))

```

DESCRIBE Each Graph

If n> 30: prop.test(x, n, p = 0.5, alternative = “two.sided”, correct=TRUE)
For the city of Baltimore, MD, use the prop.test function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe.

Conducting a one sample test for proportions using prop.test
Is the proportion of unresolved cases in Baltimore different from 50%?
```{r}
baltimore_df <- homicide_clean |> 
  filter(city_state == "Baltimore,MD") |> 
  mutate(disposition = recode(
    disposition,
    "Closed by arrest" = 0,
    "Closed without arrest" = 1,
    "Open/No arrest" = 1))

num_successes <- baltimore_df |> 
  filter(disposition == 1) |> 
  nrow()

n_sample <- nrow(baltimore_df)

output <- prop.test(x = num_successes, n = n_sample, p = 0.5, alternative = "two.sided", conf.level = 0.95, correct = FALSE)

output |> 
  broom::tidy() |> 
  select(estimate, conf.low, conf.high)

#prop.test(x = num successes, n = total cases, p = 0.5, alternative = "two.sided", conf.level = 0.95, correct = FALSE)


#fit |> 
 # broom::tidy() |> 
  #select(term, estimate, p.value) |> 
 # mutate(term = str_replace(term, "^borough", "Borough: ")) |> 
 # knitr::kable(digits = 3)



```














